Supplementary Material

### 2019-01-09 analyses/reproduce_analyses.Rmd
add seed to bootstrap to ensure reproducibility

  if(is.null(bootstraps) == FALSE){
    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

>>>>

  if(is.null(bootstraps) == FALSE){
    set.seed(34) # make sure results are reproducible
    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
